Clicks and Cliques

### 2018-12-28 papersoul.Rnw
life chunk: fix prop.res greater than 1

 prodplot(data = soul, PROJWT/3 ~CCEGRP2 + Openess, divider = c("vspine", "hspine"), subset = level == 2) + aes(fill = CCEGRP2) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.title.x = element_text(size = 15), axis.text.x = element_text(size = 15),  axis.text.y = element_text(size = 15)) + scale_fill_brewer(type = 'seq', palette = 1) 
 prodplot(data = soul, PROJWT/3 ~ CCEGRP2 + Social.Offering , divider = c("vspine", "hspine"), subset = level == 2) + aes(fill = CCEGRP2) + theme( axis.text.y = element_blank(), axis.title.y = element_blank(), axis.title.x = element_text(size = 15), axis.text.x = element_text(size = 15), legend.text = element_text(size = 15), legend.title = element_text(size = 15)) + scale_fill_brewer(type = 'seq', palette = 1, name = 'Attach level') + labs(x = "Social Offering")

@@

Data from ACS are comunity variable, computed using sampling weights by Census Bureau. 
When using data from Knight Foundation surveys, the sampling weights need to be taken into
account, if the data comes from only one year then the sampling weight is provided
in the data, when all three year survey data are used, sampling weights are divided by three 
so the total aggregate of each variable still can be consider an estimate of the comunity
total.

\subsection{Data description}
The main data set used in this paper was provided by the Knight Foundation, consisting of collected data from 47821 people over three years (2008, 2009 and 2010) in 26 communities across the United States. The data is available at http://streaming.stat.iastate.edu/dataexpo/2013/ as part of the 2013 Data Expo competition of the American Statistical Association. Additional details on the 2013 Data Expo can be found in \cite{soul2}.

@@

\begin{figure}
<<education,echo=FALSE, dependson='data'>>=
dat.aux <- census.data %>%
  select(QSB, Less.than.high.school.graduate., High.school.graduate., Some.college.or.associate.s.degree., Bachelor.s.degree.or.higher.) %>% arrange(Bachelor.s.degree.or.higher.) %>%
  mutate(QSB = reorder(QSB, Bachelor.s.degree.or.higher.)) %>%
  gather(variable, value, -QSB) %>% 
  mutate( variable = recode_factor(
      variable,
      "Less.than.high.school.graduate." = "Less High School",
      "High.school.graduate." = "High School",
      "Some.college.or.associate.s.degree." = "Some College",
      "Bachelor.s.degree.or.higher." = "Bachelor or higher"), Education.Level = variable)

prodplot(data = dat.aux, value~Education.Level + QSB, divider = c( "hspine","vspine")) + aes(fill = Education.Level) + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.y = element_blank(), axis.text.y = element_text( size = I(10)) ) + scale_fill_brewer(type = 'seq', palette = 2) + labs(x = "Education Level")
@
\caption{Product plot of education level by community, the width of each box represent the proportion of people with that education level within a community.  Communities are sorted from top to bottom by proportion of people with college degree. Big range of variation on education level among the communities. \label{edu}}
\end{figure}

@@

ggplot(census.data, aes(gini, income.pc)) + 
  geom_point(size = I(4)) + 
  geom_text(data = aux, aes(gini,income.pc, label = QSB, color = gr, hjust = h1, vjust = v1), size = I(6)) + 
  labs(y = 'Income per capita', x ='Gini') +
  theme(legend.position = "none", axis.title = element_text(size = 20),
        axis.text =  element_text(size =  20))

ggplot(census.data, aes(Bachelor.s.degree.or.higher., income.pc)) + 
  geom_point(size = I(4)) +  
  geom_text(data = aux, aes(Bachelor.s.degree.or.higher.,income.pc, label = QSB, color = gr, hjust = h2, vjust = v2), size = I(5))  + 
  labs(y = 'Income per capita', x = 'Bachelor Degree') + 
  theme(legend.position = "none", axis.title = element_text(size = 20),
        axis.text =  element_text(size =  20))
@
\caption{Scatter plot of income per capita by Gini index (left) and scatter plot of income per capita by proportion of people with bachelor degree (right). Colors identify groups based on income and Gini. \label{ecolink}}
\end{figure}

@@

As a final step in the socio-demographic characterization of the communities, cluster analysis on community characteristics was performed. For this analysis nine variables from the Census Bureau data are used: proportion of people between 18 and 21 years old (Yr.1821), proportion of people with a bachelor degree (Bachelor), the Gini inequality index (Gini), proportion of people who moved to the community after the year 2000 (New.entry), the average age of the female population (Age.Fem), the unemployment rate (Unemp), no workers rate (No.workers), home owner rate (Own.rate) and the proportion of African-Americans (Afr.pr).

@@

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!
life <- svyby(~prop.res + QD1 + CCE, ~QSB, des.wt, svymean, keep.var = TRUE, na.rm = T)
lifevar <- svyby(~prop.res + CCE, ~QSB, des.wt, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

>>>>

prodplot(data = soul, PROJWT/3 ~CCEGRP2 + Openess, divider = c("vspine", "hspine"), subset = level == 2) + aes(fill = CCEGRP2) + theme(legend.position = 'none',axis.title.y = element_blank()) + scale_fill_brewer(type = 'seq', palette = 1)

prodplot(data = soul, PROJWT/3 ~ CCEGRP2 + Social.Offering , divider = c("vspine", "hspine"), subset = level == 2) + aes(fill = CCEGRP2) + theme(axis.text.y = element_blank(),axis.title.y = element_blank()) + scale_fill_brewer(type = 'seq', palette = 1, name = 'Attach level')

@@

Data from ACS are comunity variable, computed using sampling weights by Census Bureau. 
When using data from Knight Foundation surveys, the sampling weights need to be taken into
account, if thte data comes from only one year then the sampling weight is provided
in the data, when all three year survey data are used, sampling weights are divided by three 
so the total aggregate of each variable still can be consider an estimate of the comunity
total.

\subsection{Data description}
The main data set used in this paper was provided by the Knight Foundation, consisting of collected data from 47821 people over three years (2008, 2009 and 2010) in 26 communities across the United States. The data is available at http://streaming.stat.iastate.edu/dataexpo/2013/ as part of the 2013 Data Expo competition (see \cite{soul} for additional details).

@@

\begin{figure}
<<education,echo=FALSE, dependson='data'>>=
dat.aux <- census.data %>%
  select(QSB, Less.than.high.school.graduate.,High.school.graduate.,Some.college.or.associate.s.degree.,Bachelor.s.degree.or.higher.) %>% arrange(Bachelor.s.degree.or.higher.) %>%
  mutate(QSB = reorder(QSB, Bachelor.s.degree.or.higher.)) %>%
  gather(variable, value, -QSB)

levels(dat.aux$variable) <- c('Less High School', 'High School', 'Some College', 'Bachelor or higher')
colnames(dat.aux)[2] <- 'Education.Level'

prodplot(data = dat.aux, value~Education.Level + QSB, divider = c( "hspine","vspine")) + aes(fill = Education.Level) + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.y = element_blank(), axis.text.y = element_text( size = I(10)) ) + scale_fill_brewer(type = 'seq', palette = 2)
@
\caption{Product plot of education level by community, the width of each box represent the proportion of people with that education level within a community.  Communities are sorted from top to bottom by proportion of people with college degree. Big range of variation on education level among the communities. \label{edu}}
\end{figure}

@@

ggplot(census.data, aes(gini, income.pc)) + 
  geom_point(size = I(4)) + 
  geom_text(data = aux, aes(gini,income.pc, label = QSB, color = gr, hjust = h1, vjust = v1), size = I(6)) + 
  labs(y = 'Income per capita', x ='Gini') +
  theme(legend.position = "none")

ggplot(census.data, aes(Bachelor.s.degree.or.higher., income.pc)) + 
  geom_point(size = I(4)) +  
  geom_text(data = aux, aes(Bachelor.s.degree.or.higher.,income.pc, label = QSB, color = gr, hjust = h2, vjust = v2), size = I(5))  + 
  labs(y = 'Income per capita', x = 'Bachelor Degree') + 
  theme(legend.position = "none")
@
\caption{Scatter plot of income per capita by Gini index (left) and scatter-plot of income per capita by proportion of people with bachelor degree (right). Colors identify some groups based on income and Gini. \label{ecolink}}
\end{figure}

@@

As a final step in the socio-demographic characterization of the communities, cluster analysis on community characteristics was performed. For this analysis nine variables from the Census Bureau data are used: proportion of people between 18 and 21 years old (1821.yr), proportion of people with a bachelor degree (bachelor), the Gini inequality index (Gini), proportion of people who moved to the community after the year 2000 (new.entry), the average age of the female population (age.fem), the unemployment rate (unemp), no workers rate (no.worker), home owner rate (own.rate) and the proportion of African-Americans (afr.pr).

@@

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!

life <- soul.red2 %>% 
  filter(!is.na(PROJWT), prop.res <= 1) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~prop.res + QD1 + CCE, ~QSB, 
               design = ., svymean, keep.var = TRUE, na.rm = T)

lifevar <- svyby(~prop.res + CCE, ~QSB, des.wt, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))
